---
title: "Waffle"
output: html_notebook
---

Load necessary libraries. Installation is a little tricky with some of the packages and can differ based on machine.
```{r setup}
#devtools::install_git("https://git.rud.is/hrbrmstr/waffle.git")
#install.packages("systemfonts") # may throw an error if on mac, try "brew install freetype"
#install.packages("hrbrthemes", repos = c("https://cinc.rud.is", "https://cloud.r-project.org/"))
library(waffle)
library(hrbrthemes)
library(extrafont)
library(dplyr)
library(ggthemes)
```

Plot a basic waffle plot
```{r basic_example}
parts <- c(80, 30, 20, 10)
basic <- waffle(parts, rows = 8)
ggsave("Images/BasicPlot.png", basic)
basic
```

Plot a waffle plot given a data frame
```{r data_frame_example}
df <- data.frame(
  parts = factor(rep(month.abb[1:3], 3), levels=month.abb[1:3]),
  vals = c(10, 20, 30, 6, 14, 40, 30, 20, 10),
  col = rep(c("blue", "black", "red"), 3),
  fct = c(rep("Thing 1", 3),
          rep("Thing 2", 3),
          rep("Thing 3", 3))
)

data <- df %>%
  count(parts, wt = vals) %>%
  ggplot(aes(fill = parts, values = n)) +
  geom_waffle(n_rows = 20, size = 0.33, colour = "white", flip = TRUE) +
  scale_fill_manual(
    name = NULL,
    values = c("#a40000", "#c68958", "#ae6056"),
    labels = c("Fruit", "Sandwich", "Pizza")
  ) +
  coord_equal() +
  theme_ipsum_rc(grid="") +
  theme_enhance_waffle()
ggsave("Images/DataPlot.png", data)
data
```

Install Font Awesome to your personal font folder. Location is displayed after running following code:
```{r install_glyphs}
install_fa_fonts()
```

View available glyphs from Font Awesome
```{r available_glyphs}
fa_list()
```

Load fonts into R
```{r glyphs}
extrafont::font_import()
extrafont::loadfonts(quiet = TRUE)
```

Plot a waffle plot with glyphs
```{r glyph_example}
glyph <- df %>%
  count(parts, wt = vals) %>%
  ggplot(aes(label = parts, values = n)) +
  geom_pictogram(n_rows = 10, aes(colour = parts), flip = TRUE, make_proportional = TRUE) +
  scale_color_manual(
    name = NULL,
    values = c("#a40000", "#c68958", "#ae6056"),
    labels = c("Fruit", "Sandwich", "Pizza")) +
  scale_label_pictogram(
    name = NULL,
    values = c("apple-alt", "bread-slice", "pizza-slice"),
    labels = c("Fruit", "Sandwich", "Pizza")  ) +
  coord_equal() +
  theme_ipsum_rc(grid="") +
  theme_enhance_waffle() +
  theme(legend.key.height = unit(2.25, "line")) +
  theme(legend.text = element_text(size = 10, hjust = 0, vjust = 0.75))
ggsave("Images/GlyphPlot.png", glyph)
glyph
```
```{r scaled}
storms %>% 
  filter(year >= 2010) %>% 
  count(year, status) -> storms_df

scaled <- ggplot(storms_df, aes(fill = status, values = n)) +
  geom_waffle(color = "white", size = .25, n_rows = 10, flip = TRUE) +
  facet_wrap(~year, nrow = 1, strip.position = "bottom") +
  scale_x_discrete() + 
  scale_y_continuous(labels = function(x) x * 10,
                     expand = c(0,0)) +
  ggthemes::scale_fill_tableau(name=NULL) +
  coord_equal() +
  labs(
    title = "Faceted Waffle Bar Chart",
    subtitle = "{dplyr} storms data",
    x = "Year",
    y = "Count"
  ) +
  theme_minimal(base_family = "Roboto Condensed") +
  theme(panel.grid = element_blank(), axis.ticks.y = element_line()) +
  guides(fill = guide_legend(reverse = TRUE))
ggsave("Images/ScaledPlot.png", scaled)
scaled
```

Plot a waffle plot with a transparent background
```{r transparent}
platform <- data.frame("Platform"=c('Prime Video','Netlflix','Hulu','Disney+'),"Count"=c(12354,3560,903,554))
platform$Platform <- factor(platform$Platform,levels=c('Prime Video','Netlflix','Hulu','Disney+'))

transparent <- ggplot(platform,aes(fill = Platform, values = Count/10)) +
  expand_limits(x=c(0,0), y=c(0,0)) +
  coord_equal() +
  labs(fill = NULL, colour = NULL) +
  theme_ipsum_rc(grid="") +
  theme_enhance_waffle() +
  scale_fill_manual(values=c("grey60","grey75","grey90","#111E4F")) + 
  geom_waffle(n_rows = 20, 
              size = 0, 
              radius = unit(1, "pt"),
              height = 0.8, 
              width = 0.8) +
  theme(
    legend.position = "bottom"
  )
ggsave("Images/TransparentPlot.png", transparent)
transparent
```