---
title: "Projecting Fantasy Points"
output: html_document
---

```{r}
library(foreign)
library(tidyr)
library(jtools)
library(scales)
```


#We finish by testing to see what effects age and what position you play have on your fantasy point production.
```{r}
fantasy_df <- read.csv("../data/weekly_fantasy_points.csv")
fantasy_df = fantasy_df[,!(names(fantasy_df) %in% c("X","X.1"))]
points_df <-read.csv("../data/points.csv")
points_df = points_df[,!(names(points_df) %in% c("X"))]
sum_cols <- c(names(points_df),"FPoints")

```

```{r}
season_df <- fantasy_df%>%
  dplyr::group_by(PlayerID,season, position,team,full_name,age)%>%
   dplyr::summarise_at(sum_cols, sum, na.rm=TRUE) %>%
  dplyr::ungroup()
```

```{r}
season_df$age2 <- season_df$age^2
```

#Here we are printing out a scatter plot of every player in the dataset with the X axis showing how old they are and the Y axis showing how many fantasy points they scored.
```{r}
pdf("../results/Age_FPoints.pdf")
plot(season_df$age,season_df$FPoints,xlab = 'Players Age',ylab = 'Fantasy Points',xlim = c(20,50),col=rgb(.6,0,0,0.065),pch=16)
dev.off()
```


#Here we are running a fixed effects model on the data to see what the coefficients of age and age^2 are. 
#We include age^2 because the graph of the relationship between age and fantasy points shows a downward facing parabola.
```{r}
fixed.dum <- lm(formula = FPoints ~ age + age2 +factor(position) + factor(PlayerID),data = season_df)
```

```{r}
summary(fixed.dum)
export_summs(fixed.dum,model.names="pos_Id_FE",coefs=c("age","age2","factor(position)CB","factor(position)DB","factor(position)DE","factor(position)DL","factor(position)DT","factor(position)FB","factor(position)FS","factor(position)G","factor(position)HB","factor(position)ILB","factor(position)K","factor(position)LB","factor(position)LS","factor(position)MLB","factor(position)NT","factor(position)OG","factor(position)OL","factor(position)OLB","factor(position)OT","factor(position)P","factor(position)QB","factor(position)RB","factor(position)SAF","factor(position)SS","factor(position)T","factor(position)TE","factor(position)WR"),to.file="html",file.name="../results/regression_results.html")
```